Guarded Recursive Type Theory via Sized Types

### 2019-01-10 code-oneclock-paper/latex/paper.tex
more preliminaries
Finished subsection on presheaves
Modified gitignore, clockcontexts in paper
Added label for sections for references
Work on types/context, added unicode symbols forr syntactic sugar of sigma
Modified paper.tex (removed some text)

\newunicodechar{⊤}{$\top$}
\newunicodechar{≡}{$\equiv$}
\newunicodechar{₁}{$_1$}
\newunicodechar{₂}{$_2$}
\newunicodechar{Γ}{$\Gamma$}
\newunicodechar{Δ}{$\Delta$}
\newunicodechar{Σ}{$\Sigma$}
\newunicodechar{α}{$\alpha$}
\newunicodechar{γ}{$\gamma$}
\newunicodechar{ε}{$\varepsilon$}
\newunicodechar{λ}{$\lambda$}
\newunicodechar{μ}{$\mu$}
\newunicodechar{κ}{$\kappa$}
\newunicodechar{π}{$\pi$}
\newunicodechar{⊞}{$\boxplus$}
\newunicodechar{⊠}{$\boxtimes$}
\newunicodechar{∁}{$\mathbb{C}$}
\newunicodechar{►}{$\blacktriangleright$}
\newunicodechar{▻}{$\vartriangleright$}
\newunicodechar{𝟙}{\textbf{1}}
\newunicodechar{∙}{$\cdot$}
\newunicodechar{∀}{$\forall$}
\newunicodechar{ℓ}{$\ell$}
\newunicodechar{∅}{$\varnothing$}
\newunicodechar{⟶}{$\rightarrow$}
\newunicodechar{□}{$\square$}
\newunicodechar{⇡}{$\uparrow$}
\newunicodechar{⊛}{$\circledast$}
\newunicodechar{⊎}{$\uplus$}
\newunicodechar{⟨}{$\langle$}
\newunicodechar{⟩}{$\rangle$}
\newunicodechar{∎}{$\blacksquare$}
\newunicodechar{⇒}{$\Rightarrow$}
\newunicodechar{⊕}{$\oplus$}
\newunicodechar{⊗}{$\otimes$}
\newunicodechar{∼}{$\sim$}
\newunicodechar{≈}{$\approx$}
\newunicodechar{⊔}{$\sqcup$}
\newunicodechar{⟦}{$\llbracket$}
\newunicodechar{⟧}{$\rrbracket$}
\newunicodechar{⊥}{$\bot$}
% Add more as you need them (shouldn't happen often).

@@

@@

\section{Introduction}
\cite{atkey2013productive}

\section{Preliminaries}
\input{Prelude/Basics}
%% \input{Presheaves/Presheaves}
%% \input{Presheaves/Const}
%% \input{Presheaves/Terminal}
%% \input{Presheaves/Product}
%% \input{Presheaves/Sum}
%% \input{Presheaves/Exp}
%% \input{CloTT/Structure/Contexts}
%% \input{CloTT/Structure/Types}
%% \input{CloTT/Structure/Terms}
%% \input{CloTT/Structure/DefinitionalEquality}
%% \input{CloTT/Structure/ContextOperations}
%% \input{CloTT/Structure/Subst}
%% \input{CloTT/TypeFormers/UnitType}
%% \input{CloTT/TypeFormers/SumType}
%% \input{CloTT/TypeFormers/ProductType}
%% \input{CloTT/TypeFormers/FunctionType}
%% \input{CloTT/TypeFormers/ClockQuantification}
%% \input{CloTT/TypeFormers/Later}
%% \input{CloTT/TypeFormers/LaterType}
%% \input{CloTT/TypeFormers/WeakenClock}
%% \input{CloTT/TypeFormers/Fix}
%% \input{CloTT/TypeFormers/Force}

%% \input{allcode}
\subsection{Sized Types}

\section{Deep Embedding}
\input{Prelude/Syntax}

\section{Presheaf Semantics}
\subsection{Presheaaves}
\input{Presheaves/Presheaves}

@@

\subsection{Kripke Semantics}
A context in \IC{set} is an element of \D{Set}. A context in \IC{tot}
is a preasheaf in \D{PSh}.

@@

Since we are modeling a simply typed calculus, types are interpreted
in the same ways as contexts.

@@

In \IC{set}, a term of type \Ar{A} in context \Ar{Γ} is a function
from \Ar{Γ} to \Ar{A}. In \IC{tot}, a term of type \Ar{A} in context
\Ar{Γ} is a natural transformation between the presheaves \Ar{Γ} and
\Ar{A}.

>>>>

\newunicodechar{⊤}{$\top$}
\newunicodechar{≡}{$\equiv$}
\newunicodechar{₁}{$_1$}
\newunicodechar{₂}{$_2$}
\newunicodechar{Γ}{$\Gamma$}
\newunicodechar{Δ}{$\Delta$}
\newunicodechar{Σ}{$\Sigma$}
\newunicodechar{α}{$\alpha$}
\newunicodechar{γ}{$\gamma$}
\newunicodechar{ε}{$\varepsilon$}
\newunicodechar{θ}{$\theta$}
\newunicodechar{λ}{$\lambda$}
\newunicodechar{μ}{$\mu$}
\newunicodechar{κ}{$\kappa$}
\newunicodechar{π}{$\pi$}
\newunicodechar{∈}{$\in$}
\newunicodechar{⊞}{$\boxplus$}
\newunicodechar{⊠}{$\boxtimes$}
\newunicodechar{∁}{$\mathbb{C}$}
\newunicodechar{►}{$\blacktriangleright$}
\newunicodechar{▻}{$\vartriangleright$}
\newunicodechar{𝟙}{\textbf{1}}
\newunicodechar{∙}{$\cdot$}
\newunicodechar{∀}{$\forall$}
\newunicodechar{ℓ}{$\ell$}
\newunicodechar{∅}{$\varnothing$}
\newunicodechar{⟶}{$\rightarrow$}
\newunicodechar{□}{$\square$}
\newunicodechar{⇡}{$\uparrow$}
\newunicodechar{⊛}{$\circledast$}
\newunicodechar{⊎}{$\uplus$}
\newunicodechar{⟨}{$\langle$}
\newunicodechar{⟩}{$\rangle$}
\newunicodechar{∎}{$\blacksquare$}
\newunicodechar{⇒}{$\Rightarrow$}
\newunicodechar{⊕}{$\oplus$}
\newunicodechar{⊗}{$\otimes$}
\newunicodechar{∼}{$\sim$}
\newunicodechar{≈}{$\approx$}
\newunicodechar{⊔}{$\sqcup$}
\newunicodechar{⟦}{$\llbracket$}
\newunicodechar{⟧}{$\rrbracket$}
\newunicodechar{⊥}{$\bot$}
% Add more as you need them (shouldn't happen often).

@@

\usepackage{cleveref}

@@

\section{Introduction}
\label{sec:intro}
\cite{atkey2013productive}

\section{Preliminaries}
\label{sec:prelim}
\input{Prelude/Basics}
%% \input{Presheaves/Presheaves}
%% \input{Presheaves/Const}
%% \input{Presheaves/Terminal}
%% \input{Presheaves/Product}
%% \input{Presheaves/Sum}
%% \input{Presheaves/Exp}
%% \input{CloTT/Structure/Contexts}
%% \input{CloTT/Structure/Types}
%% \input{CloTT/Structure/Terms}
%% \input{CloTT/Structure/DefinitionalEquality}
%% \input{CloTT/Structure/ContextOperations}
%% \input{CloTT/Structure/Subst}
%% \input{CloTT/TypeFormers/UnitType}
%% \input{CloTT/TypeFormers/SumType}
%% \input{CloTT/TypeFormers/ProductType}
%% \input{CloTT/TypeFormers/FunctionType}
%% \input{CloTT/TypeFormers/ClockQuantification}
%% \input{CloTT/TypeFormers/Later}
%% \input{CloTT/TypeFormers/LaterType}
%% \input{CloTT/TypeFormers/WeakenClock}
%% \input{CloTT/TypeFormers/Fix}
%% \input{CloTT/TypeFormers/Force}

%% \input{allcode}
%\subsection{Sized Types}

\section{Deep Embedding}
\label{sec:syntax}
\input{Prelude/Syntax}

\section{Presheaf Semantics}
\label{sec:presheaf_sem}
\subsection{Presheaves}
\label{sec:presheaves}
\input{Presheaves/Presheaves}

@@

\subsection{Kripke Semantics}
\label{sec:kripke}
\input{CloTT/Structure/ClockContexts}

@@

@@
